
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsbsy}

\setcounter{secnumdepth}{-1}

%% notation

\newcommand{\D}{\ensuremath{\mathbf{D}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\renewcommand{\div}{\ensuremath{\nabla \cdot}}
\newcommand{\inner}[2]{\ensuremath{(#1, #2)}}
\newcommand{\defeq}{\ensuremath{:=}}


\newcommand{\stokes}{\ensuremath{\Omega_{f}}}
\newcommand{\darcy}{\ensuremath{\Omega_{p}}}
\newcommand{\interface}{\ensuremath{\Gamma_{fp}}}


% fluid test\trial functions
\newcommand{\uf}{\ensuremath{\mathbf{u}_f}}
\newcommand{\vf}{\ensuremath{\mathbf{v}_f}}
\newcommand{\up}{\ensuremath{\mathbf{u}_p}}
\newcommand{\vp}{\ensuremath{\mathbf{v}_p}}

% pressure test\trial functions
\newcommand{\pf}{\ensuremath{p_f}}
\newcommand{\pp}{\ensuremath{p_p}}
\newcommand{\qf}{\ensuremath{q_f}}
\newcommand{\qp}{\ensuremath{q_p}}

% displacement test\trial functions
\newcommand{\disp}{\ensuremath{\boldsymbol{\eta}_p}}
\newcommand{\disptest}{\ensuremath{\boldsymbol{\xi}_p}}

% multiplier test\trial functions
\newcommand{\mult}{\ensuremath{\lambda_{\Gamma}}}
\newcommand{\multtest}{\ensuremath{\mu_{\Gamma}}}



\begin{document}

\title{Equations for system}
\maketitle


We follow \cite{ambartsumyan} very very closely.

\section{Domain}
Our domain $\Omega$ is $d=2 \text{ or } 3$-dimensional, and partitioned into \stokes and \darcy, with $\interface = \stokes \cap \darcy$ being the $(d-1)$-dimensional interface. We assume each region is connected, reasonably smooth and all that.

\section{Unknowns}
The unknowns of the system and the corresponding test functions are:

\begin{itemize}
\item \uf, \vf : free flow fluid velocity. Defined on \stokes.
\item \up, \vp : porous flow fluid velocity. Defined on \darcy.
\item \pf, \qf : free flow fluid pressure. Defined on \stokes.
\item \pp, \qp : porous flow fluid pressure. Defined on \darcy.
\item \disp, \disptest : displacement. Defined on \darcy.
\item \mult, \multtest : normal stress balance Lagrange multiplier. Defined on \interface. In \cite{ambartsumyan}, denoted $\lambda, \mu_h$.

\end{itemize}

\section{Parameters}

\begin{description}
\item[$\mu_f$] fluid viscosity (denoted $\mu$ in the \cite{ambartsumyan})
  
\item[$\lambda_p, \mu_p$] Lamé parameters. Denoted $\mu$ in \cite{ambartsumyan}.
\item[$\alpha$] Biot-Willis constant
\item[$K$] Permeability tensor. Symmetric, bounded, positive definite. Probably scalar.
\end{description}

\section{Notation}
\begin{itemize}
\item $\D(\mathbf{v}) \defeq \frac 12 (\grad \mathbf{v} + \grad \mathbf{v}^T)$
\item $\sigma_f(\uf, \pf) \defeq -\pf \mathbf{I} + 2 \mu_f \D(\uf)$
\item $\sigma_p(\disp, \pp) \defeq \lambda_p (\div \disp) + 2 \mu_p \D(\disp) - \alpha \pp \mathbf{I} $
  
\item $a_f(\uf, \vf) = \inner{2\mu \D(\uf)} {\D(\vf)}_{\stokes}$
\item $a_p^d(\up, \vp) = \inner{\mu K^{-1}\up} {\vp}_{\darcy}$
\item $a_p^e(\disp, \disptest) = \inner{\mu_p \D(\disp)} {\D(\disptest)}_{\darcy} + \inner{\lambda_p \div \disp} {\div \disptest}_{\darcy}$
  
\end{itemize}

\section{Strong formulation}
\subsection{Boundary conditions}
\subsection{Interface conditions}

\section{Variational formulation}
\subsection{Boundary conditions}






\section{Thoughts}
\begin{itemize}
\item Kent offered very gentle scepticism about using a 3-field formulation, and suggested not having \up as an unknown, using $\up = \grad \pp$ to remove it. I thought \cite{ambartsumyan} had some opinion on this, but on closer reading I can't find it, so maybe that's from another article. I should read up on this.
 
\end{itemize}

\bibliographystyle{amsalpha}
\begin{thebibliography}{99}
\bibitem{ambartsumyan}
{\sc Ambartsumyan, Ilona, et al. }, {\em "A Lagrange multiplier method for a Stokes-Biot fluid-poroelastic structure interaction model." }, arXiv preprint arXiv:1710.06750 (2017).
  
\end{thebibliography}

\end{document}
